\newlength\mystoreparindent
\newenvironment{myparindent}[1]{%
\setlength{\mystoreparindent}{\the\parindent}
\setlength{\parindent}{#1}
}{%
\setlength{\parindent}{\mystoreparindent}
}

\documentclass[a4paper]{article}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}

\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
  #1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\begin{document}

\begin{myparindent}{0pt}

Kyle Kloberdanz \newline
20 November 2021 \newline

\textbf{Exercise 1.1.1}:
Given functions $\sigma: A \rightarrow B$ and $\tau: B \rightarrow C$,
prove that if $\tau \circ \sigma$ is injective, then so is $\sigma$.

\begin{proof}
We will demonstrate a proof by contradiction. Assume $\sigma$ is not injective, then by
definition there exists two distinct values $a_1$, $a_2$ $\in A$ such that
$\sigma(a_1) = \sigma(a_2)$.
This implies that $\tau(\sigma(a_1)) = \tau(\sigma(a_2))$
which contradicts the assumption that $x \in A$, $\tau(\sigma(x))$ is an injective function.
Hence $a_1$ and $a_2$ cannot exist and $\sigma$ must be an injective function.
\end{proof}

\textbf{Exercise 1.2.2}:
Decide which of the following are equivalence relations on the set of natural numbers $\mathbb{N}$. For those
that are, prove it. For those that are not, explain why. \newline
\newline

(i) $x \sim y$ if $\norm{x - y} \le 3$ \newline
\begin{proof}
We will demonstrate a proof by counterexample.
We will demonstrate that there exists a situation such that $x \sim y$ and $y \sim z$ but $x \sim z$ is false.
Let $x, y, z \in \mathbb{N}$ and let $x = 2$, $y = 4$, and $z = 6$. \newline
\newline
We can see that for the case of $x \sim y$ that $\norm{2 - 4} \le 3$ is true. \newline
We can see that for the case of $y \sim z$ that $\norm{4 - 6} \le 3$ is true. \newline
However, we can see that for the case of $x \sim z$ that $\norm{2 - 6} \le 3$ is false. \newline
Hence, the statement is not transitive, and therefore it is not an equivalence relation.
\end{proof}

(ii) $x \sim y$ if $\norm{x - y} \ge 3$ \newline
\begin{proof}
For any $x \in \mathbb{N}, x - x = 0$. Furthermore $\norm{x - x} = 0$. Clearly 0 is less than 3,
hence the statement $\norm{x - x} \ge 3$ is false,
hence $x \sim x$ is false, which means $x \sim y$ is not reflexive and therefore not an equivalence relation. \newline
\end{proof}

(iii) $x \sim y$ if $x$ and $y$ have the same digit in the 1's place (expressed in base 10). \newline
\begin{proof}
Let the set $D$ be the set of decimal digits, which would be exactly $\{0, 1, 2, 3, 4, 5, 6, 7, 8, 9\}$.
Note that $D \subset \mathbb{N}$.
Let $x_1, y_1, z_1 \in D$ be the digit in the one's place of $x, y, z \in \mathbb{N}$ respectively.
which means that a statement such as $x_1 = y_1$ would be read as $x$ and $y$ have the
same digit in the one's place.\newline
\newline

First, for any natural number $n \in \mathbb{N}, n$ is the same as itself,
hence $x_1 = x_1$ and $y_1 = y_1$, and therefore $x \sim x$ and $y \sim y$ so it is reflexive. \newline
\newline

Second, observe that if $x \sim y$, then $x_1 = y_1$, furthermore $x_1$ is the same number as $y_1$, but then $y_1$ is the same number as $x_1$,
and hence $y \sim x$, so it is symmetric. \newline
\newline
Third, if $x \sim y$ then $x_1 = y_1$ and if $y \sim z$ then $y_1 = z_1$, then $x_1$ is the same as $y_1$ and $y_1$ is the same as $z_1$,
so $x_1$ is the same as $z_1$, and hence $x \sim z$, and therefore it is transitive. \newline
\newline
Finally, because we have shown that the relation is reflexive, symmetric, and transitive, by definition
this is an equivalence relation.
\end{proof}


(iv) $x \sim y$ if $x \ge y$ \newline
\begin{proof}
We will demonstrate a proof by counterexample. Let $x = 2$ and $y = 1$. In this scenario, $x \sim y$ because
$2 \ge 1$, however $y \sim x$ is false, because that would imply $1 \ge 2$, which is absurd,
and therefore a counterexample showing that the relation is not symmetric.
Because this relation is not symmetric, it is therefore not an equivalence relation.
\end{proof}

\textbf{Exercise 1.2.3}:
Prove that for any $f: X \rightarrow Y$, the relation $\sim_f$ defined in Example 1.2.6 is an equivalence relation.
Show that for any $x \in X$, the equivalence class of $x$ is precisely $[x] = f^{-1}(f(x))$. \newline
\newline
\textit{Note}: $f^{-1}$ refers to the \textit{preimage} of \textit{fiber} of $f$, which is defined on page 4 of your textbook.
You should \textit{not} assume that $f$ is an invertible function.
\newline

TODO \newline

\textbf{Exercise 1.2.4}:
Prove Proposition 1.2.13: If $\sim$ is an equivalence relation on $X$, then the function $\pi: X \rightarrow X/\sim$
defined by $\pi(x) = [x]$ is a surjective map, and the equivalence relation $\sim_{\pi}$ determined by $\pi$ is
precisely $\sim$. \newline

TODO \newline

\textbf{Exercise 1.3.1}:
Let $\sigma \in S_8$ be the permutation given by the $2 \times 8$ matrix \newline
\[
  \sigma =
  \begin{pmatrix}
    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
    4 & 1 & 3 & 2 & 7 & 6 & 8 & 5 \\
  \end{pmatrix}
\]
Express $\sigma, \sigma^2, \sigma^3$ and $\sigma^{-1}$ in disjoint cycle notation. \newline

TODO \newline

\textbf{Exercise 1.3.2}:
\noindent Consider $\sigma = \begin{array}{rrr} (3 & 4 & 8) \end{array}$  $\begin{array}{rrrr} (5 & 7 & 6 & 9) \end{array}$
and $\tau = \begin{array}{rrrr} (1 & 9 & 3 & 5) \end{array}$ $\begin{array}{rrrr} (2 & 7 & 4) \end{array}$
in $S_9$ expressed in disjoint cycle notation.
Compute $\sigma \circ \tau$ and $\tau \circ \sigma$, expressing both in disjoint cycle notation.

TODO \newline

\end{myparindent}
\end{document}
