\newlength\mystoreparindent
\newenvironment{myparindent}[1]{%
\setlength{\mystoreparindent}{\the\parindent}
\setlength{\parindent}{#1}
}{%
\setlength{\parindent}{\mystoreparindent}
}

\documentclass[a4paper]{article}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{amsmath}

\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
  #1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\graphicspath{ {./} }

\begin{document}

\begin{myparindent}{0pt}

Kyle Kloberdanz \newline
5 March 2022 \newline

\textbf{Exercise 2.6.3}:
Prove Proposition 2.6.8: If $(G, *)$ is a group, and $H \subset G$ is a
subgroup, then the group operation on $G$ restricts to an operation on $H$
making it into a group. \newline

\begin{proof}
  We must show that $H$ is a group. Recall a set $G$ to be a group, group it
  must satisfy the following conditions.

  (i) $*$ is associative

  (ii) there is an identity $e \in G$

  (iii) there exists an inverse $g^{-1} \in G$
  \newline

  Because were know that $H$ is a subgroup of $G$, we know by the definition Of
  a subgroup that for all $g \in H$, $g^{-1} \in H$, and therefore we know that
  there exists an inverse for every $g$ in $H$, satisfying (iii) \newline

  We also know from the definition of a subgroup, that for all $g, h \in H$ that
  $g * h \in H$. Because of this, and also from the definition that for every
  $h \in H$, that $h^{-1} \in H$, then if $h = g^{-1}$, then
  $g * h = g * g^{-1} = e$. Also, if $g = h^{-1}$ then $g * h = h^{-1} * h = e$.
  We can see that there exists an identity $e \in H$, satisfying (ii) \newline

  From the definition of a subgroup, we can see that for $f, g, h \in H$ that
  $f, g, h \in G$ and also for $x \in H$, $x = f * g * h$ that $x$ is also in
  $G$. Because we know $G$ is a group, and the operator on a group is
  associative, For $x \in G$, $x = (f * g) * h = f * (g * h)$, but because
  $x, f, g, h \in H$, then $x \in H$, $x = (f * g) * h = f * (g * h)$,
  satisfying (i), that $*$ is an associative operator for $H$. \newline

  Therefore, because we have satisfied i, ii, iii, we know that $H$ is a group
  with the operator $*$ restricted on it.
  \newline
\end{proof}

\textbf{Exercise 2.6.4}:
Prove that the roots of unity $C_n$, defined in Example 2.3.18 form a subgroup
of the group $S^1$ from Example 2.6.12. \newline
\begin{proof}
  Recall:
  \[ C_n = \{ e^{2 \pi ki / n} | k \in \{ 0, ..., n - 1 \} \} \]
  Where $k, n \in \mathbb{Z}$
  \[ S^1 = \{ e^{i \theta} | \theta \in \mathbb{R} \} \]
  Where $S^1 < \mathbb{C}^{\times}$ with multiplication. \newline

  We must demonstrate that $C_n < S^1$. \newline

  We must first show that for the set $C_n$ that $C_n \subset S^1$.
  We notice that $2 \pi k/n \in \mathbb{R}$. Hence $\{ 2 \pi k/n | k \in \{ 0, ..., n - 1 \} \} \subset \mathbb{R}$.
  Hence $\{ 2 \pi k/n | k \in \{ 0, ..., n - 1 \} \}$ is a subset of all possible values of $\theta$.
  Therefore we can see that $C_n \subset S^1$. \newline

  Next, we must show that for all $x, y \in C_n$, that $xy \in C_n$.
  Let $k, l \in \{ 0, ..., n - 1 \}$ such that $x = e^{2 \pi ik/n}$ and
  $y = e^{2 \pi il/n}$
  \[ xy = e^{2 \pi ik/n}  e^{2 \pi il/n} = e^{(2 \pi ik/n) + (2 \pi il/n)} = e^{(2\pi i/n)(k + l)} = e^{2\pi i (k + l) / n} \]

  Rewritten using Euler's Formula:
  \[ e^{2\pi i (k + l) / n} = cos(2\pi (k + l) / n) + i\ sin(2\pi (k + l) / n) \]

  Recall if $k \equiv l \pmod{n}$, then $cos(2 \pi k/n) = cos(2 \pi l/n)$ and
  $sin(2 \pi k/n) = sin(2 \pi l/n)$ \newline

  Given this property of sin and cos with respect to multiples of $2 \pi$, we
  can see that $k$ and $l$ form an equivalency class $\pmod n$, and by
  equivalency class addition, $[k] + [l] = [k + l]$,
  hence for any $x, y \in C_n$, $xy \in C_n$. \newline

  We must now show that for all $x \in C_n$, $x^{-1} \in C_n$.
  Let $x = e^{2 \pi k i / n}$, hence $x^{-1} = e^{-2 \pi k i / n}$.
  We must show that $xx^{-1} = x^{-1}x = 1$.

  \[ xx^{-1} = e^{2 \pi k i / n} e^{-2 \pi k i / n} = \frac{e^{2 \pi k i / n}}{e^{2 \pi k i / n}} = 1 \]
  \[ x^{-1}x = e^{-2 \pi k i / n} e^{2 \pi k i / n} = \frac{e^{2 \pi k i / n}}{e^{2 \pi k i / n}} = 1 \]

  Hence for all $x \in C_n$, we have shown that there exists the inverse $x^{-1}$
  such that $xx^{-1} = x^{-1}x = 1$. \newline

  Therefore, because we have shown that $C_n < S^1$, for all $x, y \in C_n$,
  that $xy \in C_n$, and for all $x \in C_n$, $x^{-1} \in C_n$, we conclude
  that $C_n < S^1$. In other words, $C_n$ is a subgroup of $S^1$

\end{proof}

\textbf{Exercise 2.6.9}:
Suppose $R$  is a ring and $X$ is a nonempty set. Complete the proof that $R^X$
forms a ring by proving

\begin{proof}
(a) that the pointwise addition on $R^X$ is commutative, \newline

  Recall, pointwise addition states $(f + g)(x) = f(x) + g(x)$ where $f, g \in R^X$
  Because for a ring $R$, $(R, +)$ forms an abelian group, and therefore addition
  is commutative. Because of this, we see that:
  \[ (f + g)(x) = f(x) + g(x) = g(x) + f(x) = (g + f)(x) \]
  Therefore pointwise addition on $R^X$ is commutative. \newline

(b) 0 is an additive identity,

  \[ (0 + f)(x) = 0(x) + f(x) = f(x) = f(x) + 0(x) = (f + 0)(x) \]
  Therefore, $0$ is an additive identity. \newline

(c) $-f$ is the additive inverse of any \newline

$f \in R^X$ (and so $(R^X, +)$ is an abelian group)
  \[ (-f + f)(x) = -f(x) + f(x) = 0 = f(x) + (-f(x)) = (f + (-f))(x) \]
  Therefore, $-f$ is the additive inverse of any $f \in R^X$ \newline

(d) multiplication distributes over addition. \newline

  Recall, pointwise multiplication states $(fg)(x) = f(x)g(x)$, where $f, g \in R^X$.
  \newline

  Let $a, b, c \in R^X$
  \[ (a + b)(x) = a(x) + b(x) \]
  \[ c(a + b)(x) = c(x) (a(x) + b(x)) \]
  \[ c(a + b)(x) = (c(x) a(x)) + (c(x) b(x)) \]
  \[ c(a + b)(x) = (c(x) a(x)) + (c(x) b(x)) \]
  \[ c(a + b)(x) = (ca)(x) + (cb)(x) \]
  \[ c(a + b)(x) = ((ca) + (cb))(x) \]

  Therefore, multiplication distributes over addition. \newline

If $R$ is a commutative ring, prove that $R^X$ is a commutative ring. \newline

  As we saw in (a), we have already shown that addition is commutative. Now
  we will demonstrate that multiplication is commutative.
  \[ (fg)(x) = f(x) g(x) = g(x) f(x) = (gf)(x) \] \newline

If $R$ has $1$, prove that the function $1(x) = 1$ is a $1$ \newline
  \[ (1f)(x) = 1(x) f(x) = f(x) = f(x) 1(x) = (f1)(x) \]
  Therefore, $1(x) = 1$ is a $1$ \newline

  Finally, because we have satisfied the conditions of a ring, we have shown
  that $R^X$ is indeed a ring.
\end{proof}

\textbf{Exercise 2.6.11}:
Suppose $\mathbb{F}$ is any field. Find a pair of linear transformations
$S, T \in \mathcal{L}(\mathbb{F}^2, \mathbb{F}^2)$ such that $ST \neq TS$.
\newline

Suppose $S(x, y) = (x + y, x + y)$ and $T(x, y) = (x + y, x + (-y))$
where $x, y \in \mathbb{Q}$

\[ ST(4, 5) = S(T(4, 5)) = S(4 + 5, 4 - 5) = S(9, -1) = (8, 8) \]
\[ TS(4, 5) = T(S(4, 5)) = T(9, 9) = (18, 0) \]
Therefore:
\[ ST(4, 5) = (8, 8) \neq TS(4, 5) = (18, 0) \]
\[ ST(4, 5) \neq TS(4, 5) \]

\textbf{Exercise 3.1.1}:
Prove part (ii) of Proposition 3.1.1: \newline

Note: for brevity, I'll omit $*$, and instead show $g * h$ as $gh$.

(i) If $g, h \in G$ and either $g * h = h$ or $h * g = h$, then $g = e$.
\begin{proof}
  \[ gh = h \]
  \[ ghh^{-1} = hh^{-1} \]
  \[ ge = e \]
  \[ g = e \]

  Also:
  \[ hg = h \]
  \[ h^{-1}hg = h^{-1}h \]
  \[ eg = e \]
  \[ g = e \]

\end{proof}

(ii) If $g, h \in G$ and $g * h = e$ then $g = h^{-1}$ and $h = g^{-1}$
\begin{proof}
  \[ gh = e \]
  \[ g^{-1}gh = g^{-1}e \]
  \[ h = g^{-1}e \]
  \[ h = g^{-1} \]

  At the same time:

  \[ gh = e \]
  \[ ghh^{-1} = eh^{-1} \]
  \[ g = eh^{-1} \]
  \[ g = h^{-1} \]
\end{proof}

\textbf{Exercise 3.1.3}:
Suppose that $G$ is a nonempty set with an associative operation $*$ such that
the following holds: \newline
1. There exists an element $e \in G$ so that $e * g = g$ for all $g \in G$, and

2. For all $g \in G$, there exists an element $g^{-1} \in G$ so that
$g^{-1} * g = e$.

Prove that $(G, *)$ is a group. \newline

The difference between this and the definition of a group is that we are only
assuming that $e$ is a “left identity”, and that elements have a “left inverse”.
Of course, we could have replaced “left” with “right” and there is an analogous
definition of a group. Hint: Start by proving that if $g \in G$ and
$g * g = g$, then $g = e$. Then prove that $g * g^{-1} = e$ (that is, the left
inverse is also a right inverse for the left identity). Finally, prove that the
left identity is also a right identity. \newline

\begin{proof}
  First, we will show that for $g \in G$, if $g * g = g$, then $g = e$. For
  brevity, I will omit the $*$.
  \[ gg = g \]
  \[ g^{-1}gg = g^{-1} g \]
  \[ eg = e \]
  \[ g = e \]

  Second, we will show that $e = g^{-1}g = gg^{-1}$
  \[ e = g^{-1}g = eg^{-1}g = (({g^{-1}})^{-1}g^{-1}) (g^{-1}g) = (({g^{-1}})^{-1}g) e = gg^{-1}e \]
  Because $e = gg^{-1}e$, and we know that $e$ is a left identity, then the only
  way for $e = gg^{-1}e$, is if $gg^{-1} = e$, which yields $e = ee$ (left identity for $e$), hence $gg^{-1} = g^{-1}g$,
  a right inverse. \newline

  Third, we will find the right identity. Because $g^{-1}g = gg^{-1}$,
  \[ g = eg = (gg^{-1})g = g(g^{-1}g) = ge = g \]

  Finally, because we know that $*$ is associative (given by the problem
  statement), and there exists an identity $e \in G$ such that
  $e * g = g * e = g$ for all $g \in G$, and for all $g \in G$, there exists
  an inverse $g^{-1} \in G$, such that $g * g^{-1} = g^{-1} * g = e$, we know
  that $G$ is indeed a group.
\end{proof}

\end{myparindent}
\end{document}
